\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
don't say MCRT twice right next to each other
"The requirement" is misplaced here..  what requirement?

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programmes 
include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
 Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical 
imaging and therapy, and space radiation environment simulations are some examples. A fundamental requirement of all of the codes is to supply a 
computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is 
typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no 
standard geometry format used across MCRT codes, with each MCRT code typically using its own unique format. The requirement of a geometry system 
that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport
 codes. Typically an MCRT code user will not have geometry in FLUKA and Geant4 for example. The file formats used for geometry are generally focused 
 on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually 
 computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not 
 amenable for MCRT programs.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
 error-free geometry files, convert between common MCRT program geometry formats and load CAD models.

>>>>

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programmes 
include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
 Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical 
imaging and therapy, and space radiation environment simulations are some examples. A fundamental requirement of all of the codes is to supply a 
computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is 
typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no 
standard geometry format used across MCRT codes, with each code typically using its own unique format. A geometry system 
that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport
 codes. Typically an MCRT code user will not have geometry in FLUKA and Geant4 for example. The file formats used for geometry are generally focused 
 on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually 
 computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not 
 amenable for MCRT programs.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
 error-free geometry files, convert between common MCRT program geometry formats and load CAD models.
